### 2020-03-06 short.body.tex
Attempted merge, but I'm confused (there's something going on with file format)

Epidemic outbreaks include a spectrum of illness, including
asymptomatic cases that can be mild and/or subclinical.
As such, symptomatic cases are the predominant focus of treatment and usually represent
the bulk of reported cases. However, infected individuals who are asymptomatic
yet infectious can be a critical, albeit poorly characterized
factor in the spread of pathogens, as well as 
present challenges for control.
Asymptomatic individuals
are hard to trace, unlikely to self-isolate,
may move outside of quarantine,  
retain normal social and travel patterns, and potentially spark new
outbreaks.
The COVID-19 outbreak has raised significant
questions regarding the role of asymptomatic cases~\citep{fauci_nejm2020}.
%For example, the incidence of asymptomatic
%infection was estimated to be
%approximately 33\% (or higher) 
%from an outbreak of COVID-19 on the Princess Cruises ship~\citep{mizumoto_2020}.
A key focus has been on estimating asymptomatic prevalence (see~\citep{mizumoto_2020}), e.g., what fraction of individuals have asymptomatic infections relative to those with symptomatic infections?
%.(i) What fraction of newly infected individuals
%have mild and/or subclinical infections rather than severe and/or
%clinical infections? (ii) What is the time-scale over which 
%individuals who have mild and/or subclinical cases remain
%infectious? (iii) How infectious are individuals
%with mild and/or subclinical infections relative to those
%with severe symptoms?  
There is currently a lot of interest in the role of asymptomatic infections in COVIF for two major reasons. 
First, the proportion of infections that are asymptomatic is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts.

Here, we focus on a third effect. 
If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key epidemiological parameters. 
Here, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability of initiating an asymptomatic case, asymptomatic case duration, and the transmission rates from asymptomatic individuals) to dynamics at the population scale. 
That is, rather than focusing on the prevalence
of asymptomatic cases, we are interested in understanding the
relevance of asymptomatic infections to secondary case production -- including
to the production of symptomatic cases.
%Our purpose is to characterize key drivers of contribution to
%secondary cases during an outbreak by `asymptomatic' individuals --
%and help characterize the relevance of asymptomatic transmission to
%outbreak dynamics and control.

>>>>

In an epidemic, symptomatic cases are the predominant focus of treatment and usually represent the bulk of reported cases. 
However, infected individuals who are asymptomatic yet infectious can be a critical factor in the spread of some pathogens.
Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns.
The COVID-19 outbreak has raised significant
questions regarding the role of asymptomatic cases~\citep{fauci_nejm2020}.
A key focus has been on estimating asymptomatic prevalence (see~\citep{mizumoto_2020}), e.g., what fraction of individuals have asymptomatic infections relative to those with symptomatic infections?
%.(i) What fraction of newly infected individuals
%have mild and/or subclinical infections rather than severe and/or
%clinical infections? (ii) What is the time-scale over which 
%individuals who have mild and/or subclinical cases remain
%infectious? (iii) How infectious are individuals
%with mild and/or subclinical infections relative to those
%with severe symptoms?

There is currently a lot of interest in the role of asymptomatic infections in COVID for two major reasons. 
First, the proportion of infections that are asymptomatic is critical to attempts to estimate the likely burden of severe outcomes (including mortality) when the virus spreads through a population.
Second, understanding the possible role of \emph{transmission} by asymptomatic individuals is crucial to planning surveillance and control efforts.

Here, we focus on a third effect. 
If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key epidemiological parameters. 
Here, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability of initiating an asymptomatic case, asymptomatic case duration, and the transmission rates from asymptomatic individuals) to dynamics at the population scale. 
That is, rather than focusing on the prevalence
of asymptomatic cases, we are interested in understanding the
relevance of asymptomatic infections to secondary case production -- including
to the production of symptomatic cases.
